---
title: "Week 12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# Same data clean up as last week.

week_12 <- shaming %>% 
  mutate(age = 2006 - birth_year) %>% 
  mutate(treatment = fct_relevel(treatment, "Control")) %>% 
  mutate(solo = ifelse(hh_size == 1, TRUE, FALSE)) %>% 
  select(-general_04, -no_of_names, -birth_year, -hh_size) 
```


## Scene 1

**Prompt:** Create a fitted model object called `fit_1` using this formula or, if you want, a formula which you prefer. You are trying to model `age` as a function of various parameters.

age ~ sex + solo + primary_04 + primary_06 + treatment + sex:solo
                    
* Is this a causal or predictive model? Why?

* Interpret the fitted model. 

* Should we keep all these variables? And the interaction term?

* Are you surprised about the meaningfulness, or lack thereof, for the treatment variables?

```{r}
fit_1 <- stan_glm(formula = age ~ sex + solo + primary_04 + primary_02 + treatment + sex:solo,
                  data = week_12,
                  refresh = 0)
```

```{r}
print(fit_1, digits = 3)
```



## Scene 2

**Prompt:** Provide a posterior probability distribution for the expected difference in ages between those who live alone and those who do not. (Hint: Given that we are asking for an expected value, use `posterior_epred()`.)


```{r}
new_obs <- tibble(solo = c(TRUE, FALSE),
                  sex = "Female",
                  primary_02 = "No",
                  primary_04 = "No",
                  treatment = "Control")

posterior_epred(fit_1,
                newdata = new_obs) %>%
  as_tibble() %>%
  rename(soloTRUE = `1`,
         soloFALSE = `2`) %>%
  mutate(diff = soloTRUE - soloFALSE) %>%
  ggplot(aes(x = diff)) +
    geom_histogram(aes(y = after_stat(count / sum(count))),
                   bins = 100,
                   alpha = 0.5) +
    labs(
      title = "Posterior Probability Distribution",
      subtitle = "Expected Difference in Age Between Those \nWho Live Alone and Those Who Don't",
      x = "Difference (Years)",
      y = "Percent"
    ) +
    scale_y_continuous(labels = scales::percent_format()) +
    theme_bw()
```





